Start with the literature: assessthe empirical evidence for the relationship between ter-rorism and political attitudes

### 2024-02-15 outputs/paper/paper.qmd
edits

A [-@main_paper] paper by Amélie Godefroidt from Norwegian University of Science and Technology published in the American Journal of Political Science delves into the moderator analyses, in order to understand how contextual factors influence the relationship between terrorism and political attitudes.   The study discusses an extended model for analyzing the relationship between terrorism and political attitudes, incorporating characteristics of manuscripts and effect sizes as moderators.               
The study examines data from various sources, and details the characteristics of studies in the field, including the types of terrorism studied, geographical focus, and methodological approaches. It notes gaps in longitudinal studies, the dominance of convenience samples, and the focus on majority group perspectives. The study finds that terrorism is associated with increased outgroup hostility, political conservatism, and rally-'round-the-flag responses, though the effects are relatively small. Although the discussion section reflects on the findings, the limitations of the existing literature still exist, such as the predominant focus on Islamist terrorism and the limited geographical scope. It calls for a more nuanced understanding of public responses to terrorism, considering the potential long-term consequences.

Our paper will follow a reproduction of Amélie Godefroidt's implications on the relationship between terrorism and political attitudes. Our paper seeks to replicate their two following research claims, (1) terrorism, whether through self-reported exposure, manipulated news exposure, anxious or angry appraisals of terrorism, or terrorist risk perceptions, is related to higher levels of outgroup hostility, political conservatism, and, to a lesser extent, rally-'round-the-flag responses, and (2) public responses to terrorism, such as outgroup hostility, political conservatism, and rally-'round-the-flag effects, are particularly noticeable in the United States and when attacks are carried out by outgroup members. Our reproduction was conducted using the statistical programming language R [@citeR]. To further enable our analysis we employed the use of the following packages: readr [@readr], here [@here], readstata13 [@readstata13], MASS [@MASS], sandwich [@sandwich], lmtest [@lmtest], dplyr [@dplyr], tidyverse [@tidyverse], jtools [@jtools], huxtable [@huxtable], list [@list], knitr [@knitr] and kableExtra [@kableExtra].

In this paper, we commences with an overview of the data source, examining the methodologies utilized in the original study, and conducting a review of the variables employed for our replication efforts. Following this, we will proceed with reproducing specific results to validate their conclusions and enhance their comprehensibility. Finally, our paper will culminate with an analysis of our findings, an exploration of ethical considerations and biases, a discussion of the limitations encountered during the replication process, and an advocacy for further research in the field.

@@

Those associations or processed data are stored in the file metaanalysis-data.xlsx. It contains 76 column and 1733 observations. A randomized selection of manuscripts (±15% of the total sample) was used to pilot the code book and make any necessary revisions.（Godefroidt, 2022) The columns can be divided into fifth major data categories. The first part of the variables are identity information of the data such as the author name, year of the study, the sample size and the general population. The second part is the political tendency and people's ethnicity with variables ranging from the percentage of people identifying as a liberal and mean to the white-muslims percentage. The third portion records the detail of each terrorist attack, including the type, date, casualties. The forth part records a series of political attitudes. For example, nationalism and institutional trust, socio-economic conservatism, support for policies that pertains an outgroup. The last part lists the technical data that will be used in meta-analysis code such as Fisher's Z correlation, regression and so on. From the original survey data, each variable correlates with a survey question asked to participants. In our reproduction, we excluded data that being used for figure3 and figure4 the moderator test. We also made some minor changes and removed insignificant data for clearer replication and viewing.

In order to better present our replication of the results, The following are measurements of public political opinions provided by the author. They are classfied into 4 categories given in the original paper. We selected some important measures

@@

In this paper we will replicate figure 2 and table2 of the original paper. Fortunately, the author has already compressed all the analysis into one coding file. We selected the corresponding part for each illustration. In terms of the analysis method, Pearson's correlation coefficient is used. According to the original paper, the manuscripts of the data they collected used various statistical method. For comparison purposes, each association is converted into a Pearson's correlation coefficient with the sampling variance. The author stressed that to "meaningfully compare and pool effect sizes, all correlations must also reflect the relation between terrorism and sociopolitical attitudes in the same direction."[@main_paper]

@@

As depicted in @fig-collection(A) and (B), scholarly interest in exploring the link between terrorism and public attitudes notably began following the 9/11 attacks, and received further impetus following the 2015–16 Islamic State (IS) attacks. Put differently, the figures imply that this research domain is significantly influenced by specific events.

@@

Table 1 demonstrates that...

```{r}
#| label: table
#| tbl-cap: "0000000000000000000"
#| echo: false
#| message: false
#| warning: false

@@

knitr::kable(
  tibble(OutcomeType = c("Outgroup hostility","Conservative shift","Rally effects"),
         k = c(645,728,360),
         j = c(126,144,72),
         Zr = c(0.126,0.132,0.090),
         LBCI = c("[0.094;0.159]","[0.108;0.156]","[0.055;0.127]")
  ),
  caption = "Relationship between Terrorism and Political Attitudes"
)
```

@@

In this reproduction we successfully replicated and proved the research result of the core findings of the original paper; the interplay between terrorism and general conservatism. Humans possess a natural tendency to favor members of their own group while displaying suspicion or hostility towards outsiders (Tajfel & Turner, 2019[@tajfel2019integrative]). This ingroup-outgroup bias serves as fertile ground for the cultivation of stereotypes, prejudice, and intergroup conflict. In the context of terrorism, extremist ideologies often exploit these psychological tendencies to demonize the targeted groups, portraying them as existential threats to the ingroup's identity and well-being. Even though political position is a person’s own opinion, but this paper used statical method and quantified the perception. After the public has witnessed a terrorism, they will shift to be more unwelcome of the region that terrorism stands for, which in this paper is mainly about Islamism. This will exacerbating pre-existing prejudices and fueling intergroup tensions. Following terrorist incidents, there is often a surge in xenophobic rhetoric, hate crimes, and discriminatory policies targeting marginalized communities (Huddy et al., 2005). This cycle of violence and retaliation perpetuates a vicious cycle of outgroup hostility, further alienating communities and creating fertile recruiting grounds for extremist ideologies.

Ideological Underpinnings Ideology plays a crucial role in shaping terrorist groups and their actions. From nationalist movements to religious extremism, various ideologies have been exploited to justify acts of terrorism. For example, groups like Al-Qaeda and ISIS espouse a distorted interpretation of Islam to justify their violent campaigns, while others, such as the Irish Republican Army (IRA), are driven by nationalist aspirations (Juergensmeyer, 2003[@juergensmeyer2003terror]). Understanding the ideological motivations behind terrorism is essential for devising effective counterterrorism strategies that address root causes rather than merely addressing symptoms. In short, addressing outgroup hostility requires a holistic approach that addresses the root causes of prejudice while promoting social cohesion and resilience against extremist narratives. By fostering empathy, understanding, and solidarity among diverse communities, we can build a more inclusive and resilient society resilient to the influence of terrorism and extremism.

>>>>

A [-@main_paper] paper by Amélie Godefroidt from Norwegian University of Science and Technology published in the American Journal of Political Science delves into the moderator analyses, in order to understand how contextual factors influence the relationship between terrorism and political attitudes.   The study discusses an extended model for analyzing the relationship between terrorism and political attitudes, incorporating characteristics of manuscripts and effect sizes as moderators.

The study examines data from various sources, and details the characteristics of studies in the field, including the types of terrorism studied, geographical focus, and methodological approaches. It notes gaps in longitudinal studies, the dominance of convenience samples, and the focus on majority group perspectives. The study finds that terrorism is associated with increased outgroup hostility, political conservatism, and rally-'round-the-flag responses, though the effects are relatively small. Although the discussion section reflects on the findings, the limitations of the existing literature still exist, such as the predominant focus on Islamist terrorism and the limited geographical scope. It calls for a more nuanced understanding of public responses to terrorism, considering the potential long-term consequences.

Our paper will follow a reproduction of Amélie Godefroidt's implications on the relationship between terrorism and political attitudes. Our paper seeks to replicate their two following research claims, (1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats and (2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians. Our reproduction was conducted using the statistical programming language R [@citeR]. To further enable our analysis we employed the use of the following packages: readr [@readr], here [@here], readstata13 [@readstata13], MASS [@MASS], sandwich [@sandwich], lmtest [@lmtest], dplyr [@dplyr], tidyverse [@tidyverse], jtools [@jtools], huxtable [@huxtable], list [@list], knitr [@knitr] and kableExtra [@kableExtra].

We begin our paper with a discussion of the data source, the methodologies employed in the original paper and a review of the variables used for our reproduction. We will then conduct a reproduction of select results to verify their findings and improve upon their accessibility. Our paper will conclude with a discussion of our findings where we conduct a case study to apply our findings to Alberta, Canada's only Province with a greater population of males, a discussion of ethical biases, limitations and a push for future research.

@@

Those associations or processed data are stored in the file metaanalysis-data.xlsx. It contains 76 column and 1733 observations. A randomized selection of manuscripts (±15% of the total sample) was used to pilot the code book and make any necessary revisions. The columns can be divided into fifth major data categories. The first part of the variables are identity information of the data such as the author name, year of the study, the sample size and the general population. The second part is the political tendency and people's ethnicity with variables ranging from the percentage of people identifying as a liberal and mean to the white-muslims percentage. The third portion records the detail of each terrorist attack, including the type, date, casualties. The forth part records a series of political attitudes. For example, nationalism and institutional trust, socio-economic conservatism, support for policies that pertains an outgroup. The last part lists the analysis technical data that will be used in meta-analysis code such as Fisher's Z correlation, Regression and so on. From the original survey data, each variable correlates with a survey question asked to participants. In our reproduction, we excluded data that being used for figure3 and figure4 the moderator test. We also made some minor changes and removed insignificant data for clearer replication and viewing.

In order to better present our replication of the results, The following are measurments of public political opinions provided by the author. They are classfied into 4 categories given in the orignal paper. We selected some important measures

@@

In this paper we will replicate figure 2 and table2 of the orginal paper. Fortunately, the author has already compressed all the analysis into one coding file. We selected the corresponding part for each illustration. In terms of the analysis method, Pearson's correlation coefficient is used. According to the orignal paper, the manuscripts of the data they collected used various statistical method. For comparison purposes, each association is converted into a Pearson's correlation coefficient with the sampling variance. The author stressed that to "meaningfully compare and pool effect sizes, all correlations must also reflect the relation between terrorism and sociopolitical attitudes in the same direction."

@@

As depicted in @fig-collection(A) and (B), scholarly interest in exploring the link between terrorism and public attitudes notably began following the 9/11 attacks, and received further impetus following the 2015–16 Islamic State (IS) attacks. After terrorist attacks, the number of studies reaches its peak level and the number of manuscripts published has increased sharply in the following years.Put differently, the figures imply that this research domain is significantly influenced by specific events.

@@

All Fisher's Z transformed correlation coefficients were used as inputs to a random-effects, three-level meta-analysis. A three-level meta-analysis assumes that observed effect sizes differ because of (1) sampling variance, (2) variance between manuscripts, and (3) variance between the correlations from within the same manuscript[@main_paper]. Therefore, the author estimated the following model:
$$
y_{ij} = \beta_0 + u_{(2)j} + u_{(3)j} + e_{ij}
$$
where any observed effect size in manuscript j ($y_{ij}$) is assumed to be equal to an overall population effect size ($\beta_0$), plus a random deviation of the mean population effect size in manuscript j from this overall population effect size ($u_{(3)j}$), plus a random deviation of the i-th population effect size in manuscript j from the mean effect in this particular manuscript ($u_{(2)ij}$), plus a random error deviation of the observed effect size from the population effect due to sampling fluctuation ($e_{ij}$)[@main_paper]. In plain language, a three-level approach allows me to consolidate an overall effect size using all 1,733 effect sizes (while properly accounting for clustering in the data), to study heterogeneity in effect sizes both between and within manuscripts, and to explore moderator variables that explain part of this variation between and within manuscripts[@main_paper].

The extent of terrorism's association with outgroup hostility, political conservatism, or rally-'round-the-flag responses can be observed in the estimated overall correlations ($Z_r$) displayed in @table. Table 2 displays the estimated overall correlations ($Z_r$). The correlations in this table are Fisher's Z-transformed, while those reported in the text below are back-transformed to their normal correlation scale (denoted as $\widehat{\rho}$) for ease of interpretation[@main_paper].

```{r}
#| label: table
#| tbl-cap: "Note. k = number of effect sizes. j = number of manuscripts. Zr = Overall Fisher's Z correlation coefficients. LBCI = Likelihood-Based Confidence Interval. The Zr estimates are considered significant when the LBCIs do not include zero."
#| echo: false
#| message: false
#| warning: false

@@

knitr::kable(
  tibble(OutcomeType = c("Outgroup hostility","Conservative shift","Rally effects"),
         k = c(645,728,360),
         j = c(126,144,72),
         Zr = c(0.126,0.132,0.090),
         LBCI = c("[0.094;0.159]","[0.108;0.156]","[0.055;0.127]")
  ),
  caption = "Relationship between Terrorism and Political Attitudes"
)#These numbers are the results from the file "Table2_calculation.qmd"
```

@table shows that terrorism is significantly associated with outgroup hostility ($\widehat{\rho}$ = 0.126), political conservatism($\widehat{\rho}$ = 0.131), and, to a lesser extent, rally-‘round-the-flag effects ($\widehat{\rho}$ = 0.090). @main_paper indicates that it is important to note that all associations are relatively small, both following conventional standards and compared to other meta-analyses in the social sciences.

@@

In this paper, we have replicated the results found by Dancygier, Egami, Jamal, and Rischke. Their analysis sought to explore the correlation between perceived mate competition in municipalities with excess males and its contributions to anti-refugee sentiments and higher crime rates in Germany. Our paper has replicated two of their major findings.

(1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats.

(2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians.

By replicating their results, we hope to apply a Canadian-facing lens to gain insights into Canadian dating markets, the geographical distribution of males and females and their potential impacts on anti-refugee sentiments.

## Canadian Relevance: Case Study on Alberta's population ratios, dating markets and anti-refugee sentiments

To investigate the relevance of Dancygier, Egami, Jamal, and Rischke's discoveries in a Canadian context, we will now explore Canada's only Province with a higher ratio of males than females.

Alberta is a Province in Canada with a total population of 4,543,111 individuals. It is the only Canadian Province that is more heavily populated by males, with a male population of 2,282,040 compared to 2,261,071 females [@statista]. Thus having a ratio of approximately 1.01, which is comparable to that of the 1st tercile in Figure 1. This means that there are about 11,000 more men than women residing in this Province. Part of the population gap can be explained by age. Alberta has a primarily young population and we typically see that as populations age they exhibit a higher female population [@edmonton_journal]. Its trades centric economy also attracts young male migrants from across Canada [@edmonton_journal].

Concerning the original paper, Alberta's population growth can be largely attributed to international immigration which has typically brought equal numbers of males and females [@edmonton_journal]. However, according to the 2021 census, 101, 650 more males are single (not married or living common law and never married) than women [@govcan]. Due to Alberta's young population, highly concentrated with men of working age, a comparison can be made to the term 'mating-aged' used in the original paper to describe males facing higher tensions of dating competition. We thus believe that similar conditions for dating and marriage markets can be made between Alberta and the German municipalities of that the 1st Tercile from Figure 1.

While population demographics are comparable between that of Alberta and the 1st tercile of German municipalities in the original paper, it is difficult to suggest that potential competition in Albertan dating and marriage markets correlates to anti-refugee sentiments and violence. However, in addressing Albertan immigrant and refugee statistics we will aim to illustrate how these patterns found in Germany can manifest in the context of Alberta. Based on the 2021-2022 Annual Population Report, Alberta welcomed 12,603 immigrants and 21,434 non-permanent residents, which include refugees [@alberta_2023].

While previous accounts have suggested that immigration has brought an equal number of males and females, it is safe to assume that Alberta is a growing population, subject to a population with a higher concentration of males [@edmonton_journal]. According to a 2018 paper, at the time 6 in 10 Canadians disagreed when asked if immigration levels were too high, with 35% believing that Canada accepts too many immigrants [@globe_mail]. However, sentiments appear less than positive in Alberta, with Albertans expressing harsher attitudes towards immigrants and refugees [@globe_mail]. 48% of Albertans at the time agreed that refugee claims are not filed from real refugees, with 62% stating that immigrants do not adopt Canadian values, about 10% higher than the national average of 51% [@globe_mail]. The Globe and Mail suggest that part of Alberta's higher anti-refugee attitudes can be attributed to its economy and fears of competition.Dancygier, Egami, Jamal, and Rischke  find that in areas where men significantly outnumber women, there are higher levels of anti-refugee hate crimes [@main_paper].

Based on these statistics, we believe that Alberta may experience a similar effect of anti-refugee sentiments in part as a result of increased immigrants/ refugees and competition in a young male-dominated population. However, as stated in their original paper, we call for further research to be conducted on this effect to better understand its implications on non-German countries.
